\documentclass[10pt, letterpaper]{article}
% Packages
\usepackage[
    ignoreheadfoot,
    top=1.5 cm,
    bottom=1.5 cm,
    left=1.5 cm,
    right=1.5 cm,
    footskip=0.8 cm
]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[dvipsnames]{xcolor}
\usepackage{fontawesome5}
\definecolor{primaryColor}{RGB}{0, 79, 144}
\usepackage[
    pdftitle={Mohamed Khayal -- Full-Stack Developer},
    pdfauthor={Mohamed Khayal},
    pdfsubject={Full-Stack Developer Resume},
    pdfkeywords={Full-Stack Developer, MERN Stack, React.js, Node.js, Next.js, MongoDB, Express.js, REST API, JWT, SQL Server},
    colorlinks=true,
    urlcolor=primaryColor
]{hyperref}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
% Settings
\pagestyle{empty}
\setcounter{secnumdepth}{0}
\setlength{\parindent}{0pt}
\renewcommand\labelitemi{\textbullet} % ATS-friendly standard bullet point
\urlstyle{same}
\titleformat{\section}{\bfseries\large}{}{0pt}{}[\titlerule]
\titlespacing{\section}{0pt}{0.24 cm}{0.12 cm}
\newenvironment{highlights}{
    \begin{itemize}[
        topsep=0.10 cm,
        parsep=0.04 cm,
        itemsep=0.04 cm,
        leftmargin=0.5 cm
    ]
}{\end{itemize}}
\begin{document}
%================ HEADER ================
\begin{center}
    {\Huge \textbf{Mohamed Khayal}} \\[4pt]
    {\Large Full-Stack Developer} \\[6pt]
    \faMapMarker* Cairo, Egypt \quad | \quad
    \faEnvelope[regular] \href{mailto:khayyalmohamed5@gmail.com}{khayyalmohamed5@gmail.com} \quad | \quad
    \faPhone* \href{tel:+201018743096}{+20 1018743096} \\[4pt]
    \faLinkedin \href{https://linkedin.com/in/mohamed-khayal-bb910b378}{linkedin.com/in/mohamed-khayal}
    \quad | \quad
    \faGithub \href{https://github.com/Mohamed-Khayyal}{github.com/Mohamed-Khayyal}
\end{center}
%================ SUMMARY ================
\section{Professional Summary}
Full-Stack Developer with hands-on experience building scalable, secure, and production-ready web applications using the MERN stack and Next.js. Skilled in designing RESTful APIs, implementing token-based authentication (JWT, refresh tokens, HttpOnly cookies), and optimizing database performance. Passionate about clean architecture, maintainable code, and delivering high-quality solutions that solve real business problems.
%================ TECHNICAL SKILLS ================
\section{Technical Skills}
\textbf{Frontend:} React.js, Next.js, HTML5, CSS3, SASS, Tailwind CSS, Bootstrap, Redux, Context API \\
\textbf{Backend:} Node.js, Express.js, RESTful APIs, JWT Authentication, Role-Based Access Control \\
\textbf{Databases:} MongoDB, Mongoose, SQL Server\\
\textbf{DevOps \& Tools:} Git, GitHub, Firebase, Cloudinary, Vercel \\
\textbf{Core Competencies:} Secure Authentication, API Design, Rate Limiting, Performance Optimization, Database Architecture, Clean Architecture
%================ EXPERIENCE ================
\section{Experience \& Training}
\textbf{Frontend Development Trainee} \hfill {2025 -- 2026} \\
\textit{DEPI -- Digital Egypt Pioneers Initiative} \\
\textit{React.js}
\begin{highlights}
    \item Completed intensive front-end web development training covering modern frontend workflows.
    \item Built production-style projects involving responsive UI.
    \item Strengthened collaboration, version control, and agile deployment practices used in real-world software projects.
\end{highlights}
\textbf{Full-Stack .NET Trainee} \hfill {2025} \\
\textit{Tuya Technology} \\
\textit{C\#, SQL Server, Entity Framework}
\begin{highlights}
    \item Built and optimized RESTful APIs, contributing to an average response-time improvement of \textbf{20\%}.
    \item Developed CRUD-based systems handling \textbf{1,000+ records} efficiently with Entity Framework and SQL Server.
    \item Designed normalized database schemas and optimized SQL queries, improving query performance by \textbf{30\%}.
    \item Implemented JWT-based authentication and role-based access control (RBAC) to secure application endpoints.
\end{highlights}
%================ PROJECTS ================
\section{Key Projects}

\textbf{Medaura \& CLYNK -- Clinic Management System (Graduation Project)} \\
\href{https://medaura-pi.vercel.app/}{Live Demo} | \href{https://github.com/Mohamed-Khayyal/Medaura}{Frontend} | \href{https://github.com/Mohamed-Khayyal/CLYNK}{Backend}
\begin{highlights}
    \item Developed a full-stack clinic management platform using Next.js, Node.js, Express.js, and SQL Server.
    \item Implemented secure JWT authentication, RBAC, appointment booking, prescriptions, and notifications.
    \item Improved platform security with rate limiting, audit logging, and analytics dashboards.
\end{highlights}

\textbf{Aetheris -- Community Forum Platform} \hfill \href{https://la2aetheris.com/}{Live Demo}
\begin{highlights}
    \item Built a full-stack community forum using React, Node.js, Express, and MongoDB Atlas.
    \item Implemented JWT authentication, admin moderation tools, and Cloudinary media uploads.
    \item Developed search, filtering, likes, and responsive user experiences.
\end{highlights}

\textbf{Games4U -- E-Commerce Platform}
\begin{highlights}
    \item Developed a MERN-based e-commerce platform for games and devices.
    \item Built authentication, cart management, dynamic pricing, and admin dashboard functionality.
    \item Applied production-ready security practices and deployment workflows.
\end{highlights}

\textbf{Medico Platform} \hfill \href{https://medico-brown-six.vercel.app/}{Live Demo}
\begin{highlights}
    \item Built a pharmacy e-commerce platform serving 200+ users with role-based authentication.
    \item Developed product browsing, ordering workflows, and responsive user interfaces.
\end{highlights}

%================ EDUCATION ================
\section{Education}
\textbf{Bachelor of Computer Science} \hfill {Oct 2022 -- Jun 2026} \\
Banha National University \hfill \textbf{GPA: 3.39 / 4.0}
%================ CERTIFICATIONS ================
\section{Certifications}
\textbf{Front-End Web Development -- DEPI (Digital Egypt Pioneers Initiative)}
\begin{highlights}
    \item Intensive training in React.js, JavaScript (ES6+), HTML5, CSS3, responsive web design, and modern front-end development practices.
\end{highlights}
\textbf{Full-Stack .NET Development -- Tuya Technology}
\begin{highlights}
    \item Training in C\#, SQL Server, Entity Framework, and scalable backend API development.
\end{highlights}
%================ LANGUAGES ================
\section{Languages}
\textbf{Arabic} -- Native \quad | \quad \textbf{English} -- Professional Working Proficiency
\end{document}
